Construction of Chebyshev nets with singularities

### 2017-09-12 Article.tex
section2

 \section{Introduction}
A global net on a surface $M$ is two families of curves such that through each point $p$ there passes exactly one curve of
each family with tangent vectors forming a basis of the tangent plane at $p$. We will denote by $\omega (p)$ the angle between
these vector at $p$ and call it angle function of the net. A global Chebyshev net (T-net in the following) is a net in which the tangent vectors to each family of line can be parallel displaced along the lines of the other family. A net is a Chebyshev net if around each point $p$, we can find a local chart
$\varphi : \Omega \subset \R^2 \mapsto M$, such that the two family of line are the line of coordinate $u \to \varphi (u, v_0)$
and $v \to \varphi (u_0, v)$ with lines parametrized by arclength
$$| \partial _u \varphi | = | \partial _v \varphi | =1.$$
When $\omega (p)=0 [\pi]$, lines are tangent and the net is no more a local chart of the surface. Singularities at these points
are of cuspidal type or shallow tails. This is well describe in a paper of E. Ghys \cite{ghys} introducing Chebyshev net on surfaces. It is not known
when there exists global T-net on compact or non compact surfaces. The angle function $\omega$ between the two family of lines appear in the metric
of local coordinates
$${\rm d}s^2={\rm d}u^2 +  2\cos \omega (u,v) {\rm d}u {\rm d}v + {\rm d}v^2$$
and the Gauss equation is related to a Sine-Gordon type equation of hyperbolic type:
$$\partial ^2 _{uv} \omega = -K(u,v) \sin 2 \omega (u,v).$$
Using Gauss Bonnet theorem which reformulate in Hazzidakis formula, it is known (see H. Hopf, \cite{HH}, Lemma 2.3) that Chebyschev
coordinates may not exist on a simply connected surface with $|\int \int K dS | \geq 2 \pi$. 
P. L. Chebyshev proved the local existence of his coordinates under an analyticity assumption. In this paper, beside the hyperbolicity property of
the Gauss equation, we will construct coordinates on the surface by finding the function $\omega$ which satisfy boundary Cauchy data conditions
on some boundary curves.

@@

 The first non local result has been proved by I. Ya. Bakelman. He  proved the existence of Chebyshev coordinates in any sector bounded by two orthogonal geodesics on a
 simply connected Aleksandrov surface under the condition that both the positive and negative integral curvatures, $\int K^+ dS$ and $\int K^- dS$ are less than $\pi /2$,   (where $K$ is the Gaussian curvature of $\surf$, $K^+=\max(K,0)$ and $K^-=\max(-K,0)$) but the net (And the surface) is not smooth. Much later, a similar result for smooth surfaces, was proved by S. L. Samelson and W. P. Dayawansa \cite{SamDaya}: under the same restriction on the curvature, they proved that on each simply connected complete smooth surface there exists a global smooth Chebyshev net. Their proof is analytical. It is well known that the existence problem for the Chebyshev coordinates can be reduced to the existence problem for a solution to a hyperbolic system of second-order partial differential equations. This system is solved in \cite{SamDaya}  by the method of a paper of Ladyzhenskaya and Shubov  \cite{Ladishenkaya}. Burago, Ivanov and Malev in \cite{burago} used Bakelman result in a sector decomposition of a surface described in a paper of Bonk and Lang \cite{bonk}. They find four sectors satisfying hypothesis of Bakelman where they construct non smooth Chebyshev net on simply connected smooth surface $M$ with  $\int K^{\pm} dS <2\pi$. Masson and Monasse in \cite{massonMonasse} improve the result of Samelson and Dayawansa by constructing smooth T-net for simply connected surfaces with $\int K^{\pm} dS <2\pi$ which is a sharp result by the lemma of H. Hopf.

@@

Let 
\begin{equation*}
  D=[0,L_u]\Times[0,L_v],\quad\text{with } L_u,L_v\in\R_\ast^+,
\end{equation*}
 and let $\gamma_u:[0,L_u]\to\surf$ and $\gamma_v:[0,L_v]\to\surf$ be
 two curves such that $\gamma_u(0)=\gamma_v(0)$, and forming an
 interior angle $\angle(\gamma_u'(0),\gamma_v'(0))\in(0,\pi)$ at their
 intersection and exterior angle
 $\psi=\pi-\angle(\gamma_u'(0),\gamma_v'(0))$. For clarity of
 exposition, throughout this section, we consider a slightly different
 notion of Chebyshev net which will refer to mappings (not necessarily
 homeomorphisms) $\varphi:D\to\surf$ satisfying
\begin{subequations}\label{eq:cheb-def-c3}
\begin{align}\label{eq:cheb-def-c3a}
|\partial_u \varphi|_g(u,v) = 1,\\
|\partial_v \varphi|_g(u,v) = 1,\label{eq:cheb-def-c3b}
\end{align}
\end{subequations}
for all $(u,v)\in D$. Furthermore, note that the orientation of the boundary curve $\gamma_v$ is reversed in this section to simplify the exposition. 
We prove in the sequel the existence and the uniqueness of a Chebyshev net $\varphi:D\to\surf$ verifying the Cauchy boundary conditions
\begin{equation}\label{eq:cond-bord-c3}
\begin{split}
  \varphi(u,0)=\gamma_u(u),\quad\forall u\in[0,L_u],\\ 
  \varphi(0,v)=\gamma_v(v),\quad\forall v\in[0,L_v].
\end{split}
\end{equation}
Since $\surf$ is a plane immersion, and since $\int_\surf{K^+}<2\pi$
and $\int_\surf{K^-}<\infty$, there exists a global bi-Lipschitz
parametrization of $\surf$~\cite{Bonk03}. In the sequel, we identify
$\surf=(\R^2,g)$. The metric $g$ satisfies the following property:
there exists $\Csurf>1$ such that for all $X\in\R^2$,
\begin{equation}\label{eq:equiv}
  \frac{1}{\Csurf}|X|\leq |X|_{g} \leq \Csurf|X|.
\end{equation}
Unless explicitly mentioned, all the considered curves are assumed to be arc-length parametrized. In the sequel, $C$ and $\tilde C$ are two generic constants whose values can change at each occurrence and we will often explicit their dependence.

Following \cite{Ghys09}, we reformulate the problem of finding a Chebyshev net $\varphi:D\to\surf$ as the problem of finding the angle distribution $\omega:D\to(0,\pi)$ between the coordinate curves defined by $\omega(u,v) = \angle(\DU\varphi, \DV\varphi)(u,v)$. With this purpose in mind, we observe that $\omega$ satisfies the following integrability condition (in the form of a modified Sine-Gordon equation) \cite{Ghys09}
\begin{equation}  \label{eq:cond-integr}
  \DUV \omega = -K(\varphi) \sin(\omega).
\end{equation}
Equivalently, $\omega$ satisfies the integrated form of \eqref{eq:cond-integr} called the Hazzidakis formula
\begin{multline}  \label{eq:hazz-form}
 \omega(u,v) = \angle\big(\gamma_u'(0),\gamma_v'(0)\big) - \int_0^u \ko_u(s)ds +
  \int_{0}^v\ko_v(s)ds\\
 - \int_0^u\int_0^vK(\varphi(s,t))\sin\big[\omega(s,t)\big]ds~dt,
\end{multline} 
for all $(u,v)\in D$, with $\ko_u:[0,L_u]\to\R$ and $\ko_v:[0,L_v]\to\R$ the geodesic curvatures of $\gamma_u$ and $\gamma_v$ respectively (see Figure \ref{fig:hazz-primal-c4}). 
\begin{figure}[!htp]
  \centering
  \begin{tikzpicture}[x=1cm,y=1cm]
    \pgfmathsetmacro{\cos}{cos(deg(60))}
    \pgfmathsetmacro{\sin}{sin(deg(60))}
    \draw[thick] (0,0) arc[start angle=150,delta angle=-30,radius=13.66] coordinate[pos=0.2] (u1) coordinate[pos=0.4] (u2) coordinate[pos=0.6] (u3) coordinate[pos=0.8] (u4);
    \coordinate (umid) at (2.3,2.7);
    \draw (umid) node[anchor=west]{$\varphi(\cdot,0){=}\gamma_u$};
    \draw[thick] (0,0) arc[start angle=-120,delta angle=-30,radius=13.66] coordinate[pos=0.2] (v1) coordinate[pos=0.4] (v2) coordinate[pos=0.6] (v3) coordinate[pos=0.8] (v4);
    \coordinate (vmid) at (-2.9,2.);
    \draw (vmid) node[anchor=east,inner sep=0pt]{$\varphi(0,\cdot){=}\gamma_v$};
   \draw[dotted] (u1) arc[start angle=-120,delta angle=-25,radius=13.66];
   \draw[dotted] (u2) arc[start angle=-120,delta angle=-20,radius=13.66];
   \draw[dotted] (u3) arc[start angle=-120,delta angle=-15,radius=13.66] coordinate[pos=0.8] (uv);
   \draw[dotted] (u4) arc[start angle=-120,delta angle=-10,radius=13.66];
   \draw[dotted] (v1) arc[start angle=150,delta angle=-25,radius=13.66];
   \draw[dotted] (v2) arc[start angle=150,delta angle=-20,radius=13.66];
   \draw[dotted] (v3) arc[start angle=150,delta angle=-15,radius=13.66];
   \draw[dotted] (v4) arc[start angle=150,delta angle=-10,radius=13.66];
   \draw[latex-] ($(uv)+(-42:0.5)$) arc[start angle=-42,delta angle=-96,radius=0.5];
   \draw ($(uv)+(-90:0.5)$) node[anchor=north]{$\omega(u,v)$};
 %   \draw[-latex] (0,0) -- (-30:1);
%    \draw ($(0,0)+(-45:0.4)$) node[anchor=north]{$\eta_1'(0)$};
 %   \draw[-latex] (0,0) -- (60:1);
%    \draw ($(0,0)+(130:0.9)$) node[anchor=west, inner sep=1pt]{$\eta_2'(0)$};
%    \draw[-latex] ($(0,0)+(-30:0.5)$) arc[start angle=-30, delta angle=90, radius=0.5];
%    \draw ($(0,0)+(15:0.5)$) node[anchor=west]{$\psi{=}\pi{-}\omega(0,0)$};
    \pgfmathsetmacro{\r}{0.5}
    \draw[-latex] (60:\r) arc[start angle=60, delta angle=90, radius=\r];
    \draw ($(90:.7)+(-.2,0)$) node{$\omega(0,0)$};
  \end{tikzpicture}
  \caption{Illustration of the coordinate curves of a Chebyshev net $\varphi$}\label{fig:hazz-primal-c4}
\end{figure}

Moreover, remark that, since $\varphi$ is a Chebyshev net, it satisfies the following property:
\begin{subequations}\label{eq:courb-geod}
\begin{align}\label{eq:courb-geoda}
\kop_u(u,v) &= -\partial_u\omega(u,v), \\\label{eq:courb-geodb}
\kop_v(u,v) &= \partial_v\omega(u,v),
\end{align}
\end{subequations}
for all $(u,v)\in D$, where $\kop_u:D\to\R$ and $\kop_v:D\to\R$ are respectively the geodesic curvatures of the $u$-coordinate curves and of the $v$-coordinate curves of $\varphi$. We obtain by combining \eqref{eq:cond-bord-c3} and \eqref{eq:courb-geod} that the angle distribution $\omega$ satisfies the boundary conditions
\begin{subequations}\label{eq:cond-bord-angle}
\begin{align}
\omega(u, 0) &= \angle(\gamma_u'(0), \gamma_v'(0)) - \int_0^u\ko_u(s)\ds,\quad\forall u\in[0,L_u],\\
\omega(0,v) &= \angle(\gamma_u'(0), \gamma_v'(0)) + \int_0^v\ko_v(s)\ds,\quad\forall v\in[0,L_v].
\end{align}
\end{subequations}
We first show that we can associate to any angle distribution
$\omega:D\to(0,\pi)$ satisfying \eqref{eq:cond-bord-angle} a unique
mapping $\varphi:=\I(\gamma,\omega):D\to\surf$ satisfying
\eqref{eq:cheb-def-c3b}, \eqref{eq:cond-bord-c3}, and
\eqref{eq:courb-geodb}. We then show that this mapping also satisfies
\eqref{eq:cheb-def-c3a} and \eqref{eq:courb-geoda} whenever $\omega$
satisfies the integrability condition \eqref{eq:cond-integr}. This
section aims at proving the following result:

\begin{theorem}[Existence and uniqueness of Chebyshev nets]\label{thm2smooth}
Let $\surf$ be a smooth immersion of the plane $\R^2$ in $\R^3$. Let
$\gamma_u:\R^+\to\surf$ and $\gamma_v:\R^+\to\surf$ be two smooth
curves with respective geodesic curvatures $\ko_u:\R^+\to\R$ and
$\ko_v:\R^+\to\R$, and such that $\gamma_u(0) = \gamma_v(0)$. Suppose
that $\psi=\pi-\angle(\gamma_u'(0),\gamma_v'(0))\in(0,\pi)$ and that
the sector $\Omega$ delimited by $\gamma_u$ and $\gamma_v$
verifies \[\int_{\gamma_u}{\ko_u^+} + \int_{\gamma_v}{\ko_v^-} +
\int_{\Omega}{K^+}<\pi-\psi \text{ and } \int_{\gamma_u}{\ko_u^-} +
\int_{\gamma_v}{\ko_v^+} + \int_{\Omega}{K^-}<\psi.\] Let
$L_u,L_v\in\R_\ast^+\cup\{+\infty\}$ and
$D=[0,L_u]\Times[0,L_v]$. Then, there exists a unique angle
distribution $\omega:D\to(0,\pi)$ verifying the boundary conditions
\eqref{eq:cond-bord-angle} and satisfying the Hazzidakis formula
\eqref{eq:hazz-form}, with $\varphi:=\I(\gamma,\omega): D\to\surf$ the
unique mapping satisfying \eqref{eq:cheb-def-c3b},
\eqref{eq:cond-bord-c3} and \eqref{eq:courb-geodb}. The mapping
$\varphi$ is a smooth Chebyshev net on $\Omega$ with angles
$0<\omega<\pi$.
\end{theorem}

We in fact prove a slightly stronger version of Theorem
\ref{thm2smooth}. Denote $\Phi^{r,k} =
C^{r}([0,L_u],C^{k}([0,L_v],\R^2))$ the space of mappings of $D$ to
$\R^2$ with $C^r$ regularity in the first variable and $C^k$
regularity in the second variable. Similarly, define
$\Theta^{r,k}=C^r([0,L_u],C^k([0,L_v],\R))$ the space of real
functions on $D$ with $C^r$ regularity in the first variable and $C^k$
regularity in the second variable. To simplify notations, set
$\Phi^{k,k}=\Phi^k$ and $\Theta^{k,k}=\Theta^k$.

\begin{theorem}[Existence and uniqueness of Chebyshev nets]\label{thm2}
Let $\surf$ be a smooth immersion of the plane $\R^2$ in $\R^3$. Let
$k\in\mathbb{N}$. Let $\gamma_u:\R^+\to\surf$ and
$\gamma_v:\R^+\to\surf$ be two curves with $C^{k+2}$ regularity, with
respective geodesic curvatures $\ko_u:\R^+\to\R$ and
$\ko_v:\R^+\to\R$, and such that $\gamma_u(0) = \gamma_v(0)$. Suppose
that $\psi=\pi-\angle(\gamma_u'(0),\gamma_v'(0))\in(0,\pi)$ and that
the sector $\Omega$ delimited by $\gamma_u$ and $\gamma_v$
verifies \[\int_{\gamma_u}{\ko_u^+} + \int_{\gamma_v}{\ko_v^-} +
\int_{\Omega}{K^+}<\pi-\psi \text{ and } \int_{\gamma_u}{\ko_u^-} +
\int_{\gamma_v}{\ko_v^+} + \int_{\Omega}{K^-}<\psi.\] Let
$L_u,L_v\in\R_\ast^+\cup\{+\infty\}$ and
$D=[0,L_u]\Times[0,L_v]$. Then, there exists a unique angle
distribution $\omega\in \Theta^{k+1}$ verifying the boundary
conditions \eqref{eq:cond-bord-angle} and satisfying the Hazzidakis
formula \eqref{eq:hazz-form}, with $\varphi:=\I(\gamma,\omega):
D\to\surf$ the unique mapping satisfying \eqref{eq:cheb-def-c3b},
\eqref{eq:cond-bord-c3} and \eqref{eq:courb-geodb}. The mapping
$\varphi$ is a Chebyshev net with $\Phi^{k+2}$ regularity on $\Omega$
with angles $0<\omega<\pi$.
\end{theorem}

\modif{Annonce du plan à retravailler}

In order to prove Theorem \ref{thm2}, we proceed along the following plan. In Section \ref{subsec:constr-param}, given the two curves $\gamma_u$ and $\gamma_v$ on $\surf$ and the angle distribution $\omega:D\to\R/2\pi\Z$ between the coordinate curves, we first construct the candidate Chebyshev net $\varphi=\I(\gamma,\omega):D\to\surf$. We then show that whenever $\varphi$ satisfies the integrability condition \eqref{eq:cond-integr}, this mapping also satisfies \eqref{eq:cheb-def-c3} under suitable regularity conditions.  In Section \ref{subsec:exist-pt-fixe}, we view the Hazzidakis formula \eqref{eq:hazz-form}, with $\varphi:=\I(\gamma,\omega)$, as a fixed-point problem on $\omega$. We show existence and uniqueness of the solution to this fixed-point equation for the curves $\gamma_u$ and $\gamma_v\big|_{[0,L_0]}:[0,L_0]\to\surf$, where $L_0\in(0,L_v]$ is a constant depending on the $C^0$-norm of the geodesic curvatures of $\gamma_u$ and $\gamma_v$. This result is called ``local existence'' in what follows. We finally extend this result to the curves $\gamma_u$ and $\gamma_v$ of arbitrary length, in the spirit of the Cauchy--Lipschitz theorem.

\section{Smoothing of a Chebyshev net with conical singularities}
\modif{A FAIRE !}

>>>>

 \section{Introduction}
A global net on a surface $M$ is two families of curves such that through each point $p$ there passes exactly one curve of
each family with tangent vectors forming a basis of the tangent plane at $p$. We will denote by $\omega (p)$ the angle between
these vector at $p$ and call it angle function of the net. A global Chebyshev net (T-net in the following) is a net in which the tangent vectors to each family of line can be parallel displaced along the lines of the other family. A net is a Chebyshev net if around each point $p$, we can find a local chart
$\varphi : \Omega \subset \R^2 \mapsto M$, such that the two family of line are the line of coordinate $u \to \varphi (u, v_0)$
and $v \to \varphi (u_0, v)$ with lines parametrized by arclength
$$| \partial _u \varphi | = | \partial _v \varphi | =1.$$
When $\omega (p)=0 [\pi]$, lines are tangent and the net is no more a local chart of the surface. Singularities at these points
are of cuspidal type or shallow tails. This is well describe in a paper of E. Ghys \cite{Ghys09} introducing Chebyshev net on surfaces. It is not known
when there exists global T-net on compact or non compact surfaces. The angle function $\omega$ between the two family of lines appear in the metric
of local coordinates
$${\rm d}s^2={\rm d}u^2 +  2\cos \omega (u,v) {\rm d}u {\rm d}v + {\rm d}v^2$$
and the Gauss equation is related to a Sine-Gordon type equation of hyperbolic type:
$$\partial ^2 _{uv} \omega = -K(u,v) \sin  \omega (u,v).$$
Using Gauss Bonnet theorem which reformulate in Hazzidakis formula, it is known (see H. Hopf, \cite{HH}, Lemma 2.3) that Chebyschev
coordinates may not exist on a simply connected surface with $|\int \int K dS | \geq 2 \pi$. 
P. L. Chebyshev proved the local existence of his coordinates under an analyticity assumption. In this paper, beside the hyperbolicity property of
the Gauss equation, we will construct coordinates on the surface by finding the function $\omega$ which satisfy boundary Cauchy data conditions
on some boundary curves.

@@

 The first non local result has been proved by I. Ya. Bakelman \cite{Bak65}. He  proved the existence of Chebyshev coordinates in any sector bounded by two orthogonal geodesics on a
 simply connected Aleksandrov surface under the condition that both the positive and negative integral curvatures, $\int K^+ dS$ and $\int K^- dS$ are less than $\pi /2$,   (where $K$ is the Gaussian curvature of $\surf$, $K^+=\max(K,0)$ and $K^-=\max(-K,0)$) but the net (And the surface) is not smooth. Much later, a similar result for smooth surfaces, was proved by S. L. Samelson and W. P. Dayawansa \cite{SamDaya}: under the same restriction on the curvature, they proved that on each simply connected complete smooth surface there exists a global smooth Chebyshev net. Their proof is analytical. It is well known that the existence problem for the Chebyshev coordinates can be reduced to the existence problem for a solution to a hyperbolic system of second-order partial differential equations. This system is solved in \cite{SamDaya}  by the method of a paper of Ladyzhenskaya and Shubov  \cite{Ladishenkaya}. Burago, Ivanov and Malev in \cite{burago} used Bakelman result in a sector decomposition of a surface described in a paper of Bonk and Lang \cite{bonk}. They find four sectors satisfying hypothesis of Bakelman where they construct non smooth Chebyshev net on simply connected smooth surface $M$ with  $\int K^{\pm} dS <2\pi$. Masson and Monasse in \cite{massonMonasse} improve the result of Samelson and Dayawansa by constructing smooth T-net for simply connected surfaces with $\int K^{\pm} dS <2\pi$ which is a sharp result by the lemma of H. Hopf.

@@

We consider a complete and simply connected immersed surface. Let 
$ D=[0,L_u]\Times[0,L_v],\quad\text{with } L_u,L_v\in\R_\ast^+$,
and let $\gamma_u:[0,L_u]\to\surf$ and $\gamma_v:[0,L_v]\to\surf$ be
 two curves such that $\gamma_u(0)=\gamma_v(0)$, and forming an
 interior angle $\angle(\gamma_u'(0),\gamma_v'(0))\in(0,\pi)$ at their
 intersection and exterior angle
 $\psi=\pi-\angle(\gamma_u'(0),\gamma_v'(0))$. For clarity of
 exposition, throughout this section, we consider a slightly different
 notion of Chebyshev net which will refer to mappings (not necessarily
 homeomorphisms) $\varphi:D\to\surf$ satisfying
\begin{subequations}\label{eq:cheb-def-c3}
\begin{align}\label{eq:cheb-def-c3a}
|\partial_u \varphi|_g(u,v) = 1,\\
|\partial_v \varphi|_g(u,v) = 1,\label{eq:cheb-def-c3b}
\end{align}
\end{subequations}
for all $(u,v)\in D$. Furthermore, note that the orientation of the boundary curve $\gamma_v$ is reversed in this section to simplify the exposition. 
We prove in the sequel the existence and the uniqueness of a Chebyshev net $\varphi:D\to\surf$ verifying the Cauchy boundary conditions
\begin{equation}\label{eq:cond-bord-c3}
\begin{split}
  \varphi(u,0)=\gamma_u(u),\quad\forall u\in[0,L_u],\\ 
  \varphi(0,v)=\gamma_v(v),\quad\forall v\in[0,L_v].
\end{split}
\end{equation}
Since $\surf$ is a plane immersion, and since $\int_\surf{K^+}<2\pi$
and $\int_\surf{K^-}<\infty$, there exists a global bi-Lipschitz
parametrization of $\surf$~\cite{Bonk03} and we identify
$\surf=(\R^2,g)$ such that there exists $\Csurf>1$ such that for all $X\in\R^2$,
\begin{equation}\label{eq:equiv}
  \frac{1}{\Csurf}|X|\leq |X|_{g} \leq \Csurf|X|.
\end{equation}

Following \cite{Ghys09}, we reformulate the problem of finding a Chebyshev net $\varphi:D\to\surf$ as the problem of finding the angle distribution $\omega:D\to(0,\pi)$ between the coordinate curves defined by $\omega(u,v) = \angle(\DU\varphi, \DV\varphi)(u,v)$. With this purpose in mind, we observe that $\omega$ satisfies the integrability condition (in the form of a modified Sine-Gordon equation) \cite{Ghys09}
\begin{equation}  \label{eq:cond-integr}
  \DUV \omega = -K(\varphi) \sin(\omega).
\end{equation}
Equivalently, $\omega$ satisfies the integrated form Gauss Bonnet formula of \eqref{eq:cond-integr} called the Hazzidakis formula
\begin{multline}  \label{eq:hazz-form}
 \omega(u,v) = \angle\big(\gamma_u'(0),\gamma_v'(0)\big) - \int_0^u \ko_u(s)ds +
  \int_{0}^v\ko_v(s)ds\\
 - \int_0^u\int_0^vK(\varphi(s,t))\sin\big[\omega(s,t)\big]ds~dt,
\end{multline} 
for all $(u,v)\in D$, with $\ko_u:[0,L_u]\to\R$ and $\ko_v:[0,L_v]\to\R$ the geodesic curvatures of $\gamma_u$ and $\gamma_v$ respectively (see Figure \ref{fig:hazz-primal-c4}). 
\begin{figure}[!htp]
  \centering
  \begin{tikzpicture}[x=1cm,y=1cm]
    \pgfmathsetmacro{\cos}{cos(deg(60))}
    \pgfmathsetmacro{\sin}{sin(deg(60))}
    \draw[thick] (0,0) arc[start angle=150,delta angle=-30,radius=13.66] coordinate[pos=0.2] (u1) coordinate[pos=0.4] (u2) coordinate[pos=0.6] (u3) coordinate[pos=0.8] (u4);
    \coordinate (umid) at (2.3,2.7);
    \draw (umid) node[anchor=west]{$\varphi(\cdot,0){=}\gamma_u$};
    \draw[thick] (0,0) arc[start angle=-120,delta angle=-30,radius=13.66] coordinate[pos=0.2] (v1) coordinate[pos=0.4] (v2) coordinate[pos=0.6] (v3) coordinate[pos=0.8] (v4);
    \coordinate (vmid) at (-2.9,2.);
    \draw (vmid) node[anchor=east,inner sep=0pt]{$\varphi(0,\cdot){=}\gamma_v$};
   \draw[dotted] (u1) arc[start angle=-120,delta angle=-25,radius=13.66];
   \draw[dotted] (u2) arc[start angle=-120,delta angle=-20,radius=13.66];
   \draw[dotted] (u3) arc[start angle=-120,delta angle=-15,radius=13.66] coordinate[pos=0.8] (uv);
   \draw[dotted] (u4) arc[start angle=-120,delta angle=-10,radius=13.66];
   \draw[dotted] (v1) arc[start angle=150,delta angle=-25,radius=13.66];
   \draw[dotted] (v2) arc[start angle=150,delta angle=-20,radius=13.66];
   \draw[dotted] (v3) arc[start angle=150,delta angle=-15,radius=13.66];
   \draw[dotted] (v4) arc[start angle=150,delta angle=-10,radius=13.66];
   \draw[latex-] ($(uv)+(-42:0.5)$) arc[start angle=-42,delta angle=-96,radius=0.5];
   \draw ($(uv)+(-90:0.5)$) node[anchor=north]{$\omega(u,v)$};
 %   \draw[-latex] (0,0) -- (-30:1);
%    \draw ($(0,0)+(-45:0.4)$) node[anchor=north]{$\eta_1'(0)$};
 %   \draw[-latex] (0,0) -- (60:1);
%    \draw ($(0,0)+(130:0.9)$) node[anchor=west, inner sep=1pt]{$\eta_2'(0)$};
%    \draw[-latex] ($(0,0)+(-30:0.5)$) arc[start angle=-30, delta angle=90, radius=0.5];
%    \draw ($(0,0)+(15:0.5)$) node[anchor=west]{$\psi{=}\pi{-}\omega(0,0)$};
    \pgfmathsetmacro{\r}{0.5}
    \draw[-latex] (60:\r) arc[start angle=60, delta angle=90, radius=\r];
    \draw ($(90:.7)+(-.2,0)$) node{$\omega(0,0)$};
  \end{tikzpicture}
  \caption{Illustration of the coordinate curves of a Chebyshev net $\varphi$}\label{fig:hazz-primal-c4}
\end{figure}

Moreover, remark that, since $\varphi$ is a Chebyshev net, it satisfies the following property:
\begin{subequations}\label{eq:courb-geod}
\begin{align}\label{eq:courb-geoda}
\kop_u(u,v) &= -\partial_u\omega(u,v), \\\label{eq:courb-geodb}
\kop_v(u,v) &= \partial_v\omega(u,v),
\end{align}
\end{subequations}
for all $(u,v)\in D$, where $\kop_u:D\to\R$ and $\kop_v:D\to\R$ are respectively the geodesic curvatures of the $u$-coordinate curves and of the $v$-coordinate curves of $\varphi$. We obtain by combining \eqref{eq:cond-bord-c3} and \eqref{eq:courb-geod} that the angle distribution $\omega$ satisfies the boundary conditions
\begin{subequations}\label{eq:cond-bord-angle}
\begin{align}
\omega(u, 0) &= \angle(\gamma_u'(0), \gamma_v'(0)) - \int_0^u\ko_u(s)\ds,\quad\forall u\in[0,L_u],\\
\omega(0,v) &= \angle(\gamma_u'(0), \gamma_v'(0)) + \int_0^v\ko_v(s)\ds,\quad\forall v\in[0,L_v].
\end{align}
\end{subequations}
We will show that we can associate to any angle distribution
$\omega:D\to(0,\pi)$ satisfying \eqref{eq:cond-bord-angle} a unique
mapping $\varphi:=\I(\gamma,\omega):D\to\surf$ satisfying
\eqref{eq:cheb-def-c3b}, \eqref{eq:cond-bord-c3}, and
\eqref{eq:courb-geodb}. We then show that this mapping also satisfies
\eqref{eq:cheb-def-c3a} and \eqref{eq:courb-geoda} whenever $\omega$
satisfies the integrability condition \eqref{eq:cond-integr}. We prove the following result:

\begin{theorem}[Existence and uniqueness of smooth Chebyshev nets in a sector]\label{thm2smooth}
Let $\surf$ be a smooth immersion of the plane $\R^2$ in $\R^3$. Let
$\gamma_u:\R^+\to\surf$ and $\gamma_v:\R^+\to\surf$ be two smooth
curves with respective geodesic curvatures $\ko_u:\R^+\to\R$ and
$\ko_v:\R^+\to\R$, and such that $\gamma_u(0) = \gamma_v(0)$. Suppose
that $\psi=\pi-\angle(\gamma_u'(0),\gamma_v'(0))\in(0,\pi)$ and that
the sector $\Omega$ delimited by $\gamma_u$ and $\gamma_v$
verifies \[\int_{\gamma_u}{\ko_u^+} + \int_{\gamma_v}{\ko_v^-} +
\int_{\Omega}{K^+}<\pi-\psi \text{ and } \int_{\gamma_u}{\ko_u^-} +
\int_{\gamma_v}{\ko_v^+} + \int_{\Omega}{K^-}<\psi.\] Let
$L_u,L_v\in\R_\ast^+\cup\{+\infty\}$ and
$D=[0,L_u]\Times[0,L_v]$. Then, there exists a unique angle
distribution $\omega:D\to(0,\pi)$ verifying the boundary conditions
\eqref{eq:cond-bord-angle} and satisfying the Hazzidakis formula
\eqref{eq:hazz-form}, with $\varphi:=\I(\gamma,\omega): D\to\surf$ the
unique mapping satisfying \eqref{eq:cheb-def-c3b},
\eqref{eq:cond-bord-c3} and \eqref{eq:courb-geodb}. The mapping
$\varphi$ is a smooth Chebyshev net on $\Omega$ with angles
$0<\omega<\pi$.
\end{theorem}

\begin{proof}[Proof of Proposition \ref{prop:sector}]
  Using Theorem \ref{thm:exist-cond-integr-c5}, we infer that there exists a unique angle distribution $\omega:(\R^+)^2\to\R/2\pi\Z$ satisfying the Hazzidakis formula \eqref{eq:hazz2-c4}, with $\varphi:(\R^+)^2\to\surf$ the unique mapping satisfying the boundary conditions \eqref{eq:bound-cond-c4} and the properties presented in the theorem.
Then, using the continuity of the angle distribution $\omega$ and $\omega(0,0)=\pi-\psi\in(0,\pi)$, we infer that there exists $\tilde L_1,\tilde L_2>0$ such that $\omega(u,v)\in(0,\pi)$ for all $(u,v)\in[0,\tilde L_1]\Times[0,\tilde L_2]$. Hence, by Theorem \ref{thm:exist-cond-integr-c5}, the mapping $\varphi$ satisfies \eqref{eq:def-cheb3-c5} for all $(u,v)\in[0,\tilde L_1]\Times[0,\tilde L_2]$. Then, in the same manner as in the proof of Lemma \ref{lem:homeo}, we obtain that $\varphi:(\R^+)^2\to\sect$ is a Chebyshev net. Suppose finally that $\tilde\varphi:(\R^+)^2\to\surf$ is a Chebyshev net satisfying the boundary conditions \eqref{eq:bound-cond-c4}. Then, using Property \ref{prop:hazz-form}, we obtain that the angle distribution $\tilde\omega:(\R^+)^2\to(0,\pi)$ defined by $\tilde\omega=\angle(\DU\tilde\varphi,\DV\tilde\varphi)(u,v)$, for all $(u,v)\in(\R^+)^2$, satisfies the Hazzidakis formula \eqref{eq:hazz2-c4}. We deduce from Theorem \ref{thm:exist-cond-integr-c5} that $\varphi=\tilde\varphi$. This concludes the proof.
\end{proof}

%%Theoreme d'existence avec regularite
